DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
updated EMSOFT'17 title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}

\begin{abstract}
We present an automated approach implemented as a MATLAB Toolbox to synthesize stable and safe digital-control systems for physical plants represented as linear and time invariant models. The tool developed in the current paper is named as DSSynth (Digital-Systems Synthesis), which is a MATLAB Toolbox that synthesizes digital controllers w.r.t. the stability specification, considering finite word-length (FWL) effects for physical plants represented by transfer-function or state-space equations. DSSynth considers fixed-point numerical representation for the digital controller and dynamic input ranges for the closed-loop control system. Currently, there are two versions of the DSSynth toolbox: command-line and MATLAB application.
\end{abstract}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{synthesis-flow.pdf}
\caption{Digital-Control Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

>>>>

\title{DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox}

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital System Synthesis), to synthesize stable and safe digital-control 
systems for physical plants represented as linear time-invariant
systems with single-input and single-output. DSSynth synthesizes digital 
controllers w.r.t. the stability and safety specifications, considering finite word-length 
effects for physical plants represented by transfer-function or state-space 
equations. DSSynth considers fixed-point numerical representation for the 
digital controller and dynamic input ranges for the closed-loop control system. 
Currently, there are two DSSynth toolbox versions: command-line and 
MATLAB application. The resulting toolbox enables application of synthesis to 
real-world systems by control engineers.
\end{abstract}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
\caption{Digital-Control Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}
